Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-02 Latex Source/paper.tex
change typing images

\subsection{Eye Tracking and Quantified Behavioral Test}
% Citations about eye tracking and QBTest here

@@

\begin{figure}
  \includegraphics[width=0.3\textwidth]{typing_test_1}
  \caption{Starting window of typing test}
  \Description{Image of the starting windows of the typing test}
\end{figure}

\begin{figure}
  \includegraphics[width=0.3\textwidth]{typing_test_2}
  \caption{Test started}
  \Description{Image of the test with the lyrics that the user will type}
\end{figure}

\begin{figure}
  \includegraphics[width=0.3\textwidth]{typing_test_3}
  \caption{Test finished}
  \Description{Image of the finished test}
\end{figure}

@@

\subsection[short]{Participants}
Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

@@

\subsection[short]{Design}
Design

>>>>

\subsection{Eye Tracking and Quantified Behavioral Test}
Citations about eye tracking and QBTest here

@@

% \begin{figure}
%   \includegraphics[width=0.3\textwidth]{typing_test_1}
%   \caption{Starting window of typing test}
%   \Description{Image of the starting windows of the typing test}
% \end{figure}

% \begin{figure}
%   \includegraphics[width=0.3\textwidth]{typing_test_2}
%   \caption{Test started}
%   \Description{Image of the test with the lyrics that the user will type}
% \end{figure}

% \begin{figure}
%   \includegraphics[width=0.3\textwidth]{typing_test_3}
%   \caption{Test finished}
%   \Description{Image of the finished test}
% \end{figure}

\begin{figure}
  \includegraphics[width=\textwidth]{typingTest}
  \caption{Typing Test Screenshots}
  \Description{Images of what the user will see in the typing test}
\end{figure}

@@

@@

\subsection[short]{Participants and Design}
Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.
